---
title: "package:rlang"
output:
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        theme: flatly
        css: mycss.css
        code_folding: show
        include:
            - in_header: in_head.html
        df_print: "paged"

---

# Load library

```{r setup, message=FALSE}
config <- yaml::read_yaml("config.yaml")
for (p in config$LIBS$CRAN) {
  if (!require(p, character.only = TRUE)) {
    install.packages(p)
  }
  require(p, character.only = TRUE)
}
packageVersion("fs")
```



# Introduction

- 文字列には`sym`
- リテラルには`quo`, `enquo`

# Usage

## dplyr-recipes

[Tidy evaluation, most common actions](https://edwinth.github.io/blog/dplyr-recipes/)


### bare to quosure:quo

```{r}
bare_to_quo <- function(x, var) {
  x %>%
    select(!!var) %>%
    head(1)
}
bare_to_quo(mtcars, quo(cyl))
```

### bare to quosure in function : enquo 

```{r}
bare_to_quo_in_func <- function(x, var) {
  var_enq <- enquo(var)
  x %>% 
    select(!!var_enq) %>%
    head(1)
}
bare_to_quo_in_func(mtcars, mpg)
```

### quosure to a name: quo_name

```{r}
bare_to_name <- function(x, nm) {
  nm_name <- quo_name(nm)
  x %>% 
    mutate(!!nm_name := 42) %>% 
    head(1) %>% 
    select(!!nm)
}
bare_to_name(mtcars, quo(this_is_42))
```

```{r}
test <- function (x, nm) {
  quo_nm <- enquo(nm)
  x %>% 
    mutate(quo_nm := Sepal.Length + 10) %>% 
    head(1)
}
test(iris, a)
```


### quosure to text: quo_text

```{r}
quo_to_text <- function(x, var) {
  var_enq <- enquo(var)
  glue::glue("The following column, was selected: {rlang::quo_text(var_enq)}")
}
quo_to_text(mtcars, cyl)
```

### character to name: sym

```{r}
char_to_quo <- function(x, var)  {
  var_enq <- rlang::sym(var)
  x %>% 
    select(!!var_enq) %>% 
    head(1)
}
char_to_quo(mtcars, "vs")
```

### multiple bares to quosure: quos

```{r}
bare_to_quo_mult <- function (x, ...) {
  grouping <- quos(...)
  x %>% 
    group_by(!!!grouping) %>%
    summarise(nr = n())
}
bare_to_quo_mult(mtcars, vs, cyl)
```

```{r}
bare_to_quo_mult <- function (x, ...) {
  grouping <- enquos(...)
  x %>% 
    group_by(!!!grouping) %>%
    summarise(nr = n())
}
bare_to_quo_mult(mtcars, vs, cyl)
```

### multiple characters to names: syms

```{r}
bare_to_quo_mul_chars <- function (x, ...) {
  grouping <- rlang::syms(...)
  x %>% group_by(!!!grouping) %>% summarise(nr = n())
}
bare_to_quo_mul_chars(mtcars, list("vs", "cyl"))
```
```{r}
bare_to_quo_mul_chars <- function (x, ...) {
  grouping <- rlang::syms(list(...))
  x %>% group_by(!!!grouping) %>% summarise(nr = n())
}
bare_to_quo_mul_chars(mtcars, "vs", "cyl")
```


### quoting full expression 



```{r}
filter_func <- function (x, filter_exp) {
  filter_exp_enq <- enquo(filter_exp)
  x %>% filter(!!filter_exp_enq)
}
filter_func(mtcars, hp == 93)
```




### quoting full expression in a character: parse_expr

文字列をパースして表現式を扱うことが可能である. 


```{r}
filter_by_char <- function (x, char) {
  func_call <- rlang::parse_expr(char); print(func_call)
  x %>% filter(!!func_call) 
}
filter_by_char(mtcars, "cyl == 6") %>%  head(1)

```

