---
title: "package : dplyr"
output:
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        theme: flatly
        css: mycss-best.css
        code_folding: show
        include:
            - in_header: in_head.html
        df_print: "paged"
        number_section: true
---



```{r setup, include=FALSE}
target_libs <- c("tidyverse", "palmerpenguins")
for (lib in target_libs) {
    if (!require(lib, character.only = TRUE)) {
        try({install.packages(lib); library(lib, character.only = TRUE)})
    }
}

```


# Original Tips

## across
acrossを使うことによりselectの構文がsummariseやmutateで用いることができる. 
これにより，特定のカラムを選択，あるいは，除去した上で関数を当てることができる. 
これにより，mutate_if, summarise_if,などは必要なくなるというイメージで良いのかな?

```{r}
penguins %>%
  group_by(species) %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE))
```

関数はlistに入れることで複数当てることができる. 
またこのとき，名前をカラムや関数名を使い指定することができる. 

```{r}
penguins %>% 
  filter(complete.cases(.)) %>%
  group_by(species) %>%
  summarise(across(ends_with("_mm"), list(men = mean, med = median), na.rm = TRUE, .names = "{.col}_{.fn}"))
```

purrrのような構文も使える. 

```{r}
penguins %>% 
  mutate(across(ends_with("_mm"), ~ .x * 1000))
```


## c_across

`rowwise`の場合に扱うことが可能である. 
使いどころ

```{r}
penguins %>% 
  rowwise() %>%
  transmute(
    sum = sum(c_across(ends_with("_mm"))), 
    sd  = sd(c_across(ends_with(("_mm"))))
  )
```


## Context dependent expressions

- n() gives the current group size.
- cur_data() gives the current data for the current group (excluding grouping variables).
- cur_data_all() gives the current data for the current group (including grouping variables)
- cur_group() gives the group keys, a tibble with one row and one column for each grouping variable.
- cur_group_id() gives a unique numeric identifier for the current group.
- cur_group_rows() gives the row indices for the current group.
- cur_column() gives the name of the current column (in across() only).

data.table de


cur_data() <-> .SD
cur_group_id() <-> .GRP
cur_group() <-> .BY
cur_group_rows() <-> .I


```{r}
penguins %>% 
  group_by(species) %>% 
  summarise(n())
```
```{r}
tmp <- 
  penguins %>% 
  group_by(species) %>% 
  summarise(a = list(cur_data()))

tmp$a[[1]]
```

```{r}
tmp <- 
  penguins %>% 
  group_by(species) %>% 
  summarise(a = list(cur_data_all()))

tmp$a[[1]]
```




```{r}
tmp <- 
  penguins %>% 
  group_by(species) %>% 
  summarise(a = list(cur_group()))

tmp$a[[1]]
```



```{r}
tmp <- 
  penguins %>% 
  group_by(species) %>% 
  summarise(a = list(cur_group_id()))

tmp$a[[1]]
```





```{r}
tmp <- 
  penguins %>% 
  group_by(species) %>% 
  summarise(a = list(cur_group_rows()))

tmp$a[[1]]
```



```{r}
# across only
tmp <- 
  penguins %>% 
  summarise(across(where(is.numeric), ~ cur_column()))


tmp

```


